---
title: "Annual Report"
format: 
  html:
    self-contained: true
editor: visual
params:
  dbPath: "path-to-database"
  startDate: "2023-01-01"
  endDate: "2023-12-31"
  author: "Gandalf"
---

## Middle Earth Annual Report

```{r, results = "hide", fig.keep = "none"}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE

# load required packages
library(AMMonitor)
  
dbPath <- params$dbPath
startDate <- params$startDate
endDate <- params$endDate
author <- params$author

# connect to the database
conx <-  AMMonitor::dbSetCon(dbPath)

# run dbGetSummary
results <- AMMonitor::dbGetSummaryData(
 con = conx,
 m_dates = c(startDate, endDate),
 disconnect = TRUE
)

tableresults <- AMMonitor::dbTableSummary(summary_data = results)

plotresults <- AMMonitor::dbPlotSummary(
  summary_data = results,
  map_database = 'state',
  regions = 'vermont')

```

This annual report documents wildlife monitoring activities in Middle Earth from `r startDate` to `r endDate`. The figures and tables were generated from the `dbGetSummaryData()`, `dbPlotSummary()`, and `dbTableSummary()` functions from the R package, *AMMonitor.* The report was generated from a Quarto script.

## Field Visits

Autonomous monitoring units were deployed at `r nrow(results$locations)` in Middle Earth, where devices captured wildlife on trail cameras and audio recorders (Figure 1).

```{r, eval = TRUE, echo = FALSE}

plotresults$gg_locations_map + 
  ggplot2::labs(
    title = "",
    caption = paste0(
      'Figure 1: Map of Locations for Middle Earth Wildlife Study \nbetween ',
      startDate, ' and ', endDate)) +
  ggplot2::theme(
    plot.caption = ggplot2::element_text(
      hjust = 0, 
      size = 12))
```

Field technicians made a total of `r nrow(results$media_visits)` visits to monitoring stations to collect media files (Table 1).

```{r }
#| cap-location: top
#| echo: FALSE
tableresults$media_visits_year_location |>
  gt::tab_options(
    container.width = 500,
    table.align = 'center'
  ) |>
  gt::tab_caption(caption = 'Table 1.')

```

## Media Files

At the monitoring locations, a total of `r nrow(results$media)` files were captured in the report time period (Table 2).

```{r}
#| echo: FALSE

tableresults$media_count_year_type |>
  gt::tab_options(
    container.width = 500,
    table.align = 'center'
  ) |>
  gt::tab_caption(caption = 'Table 2')

```

## Annotations

Media files (camera images and audio files) were labeled by both hobbits and machine learning models. Hobbit labeling was done with the *AMMonitor* shiny interface, in which a hobbit manually inspected media files and identified monitoring targets within. Annotations per tagger for all taxa are shown in Figure 2.

```{r}
#| echo: FALSE
#| eval: TRUE

plotresults$gg_annotations_personid_keysp + 
  ggplot2::labs(title = "",
                caption = 'Figure 2: Annotations per person for all taxa.') +
  ggplot2::theme(plot.caption = ggplot2::element_text(
    hjust = 0,
    size = 12)
  )

```

## Machine Learning Detections

The media collected by monitoring units were also labeled by machine learning models. For the Middle Earth monitoring program, `r length(unique(results$modelverifications$fk_modelid))` machine models are used. A total of `r nrow(results$modeloutputs)` model outputs were returned on media from within the report time period (Table 3).

```{r}
#| echo: FALSE
tableresults$modeloutputs_year |>
  gt::tab_options(
    container.width = 500,
    table.align = 'center'
  ) |>
  gt::tab_caption(caption = 'Table 3.')
```

## Summary

In summary, it was a great year for the Middle Earth wildlife monitoring program. Our focus for the next year will be building species distribution models from the hobbit- and machine-tagged data.

Respectfully submitted,

```{r}
#| echo: FALSE
message(params$author)
```
